Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-06-28 latex/ms.tex
modify Fig.1, #3

The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}n_{\rm O,2}$ and $n_{\rm O,1}n_{\rm P,2}$ comparisons, respectively). As depicted in {\bf Fig~\ref{cartoon}}, X offspring and Y parents are sampled in the population 1 and X offspring and Y parents are sampled in the population 1, and X HS and Y PO pairs found between the two populations are observed. In addition, X and Y PO pairs found within the same population are observed, which are available to estimate parent numbers, as explain the next section. In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs.

@@

\newcommand{\figcapa}{Example of relationships between mothers and their offspring number. The open, gray, and filled circles represent mothers, their eggs, and their offspring, respectively. The area of an open circle indicates the degree of reproductive potential of each mother (i.e., $\lambda_i$). The dotted and thin arrows denote mother--egg and egg--offspring relationships, respectively. The symbol x denotes a failure to survive at sampling. Sampled individuals are denoted with squares. Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm P, 2}=4$, $n_{\rm O, 1}=4$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$. The numbers of kinship pairs: $H_{\rm PO, 1}=1$, $H_{\rm PO, 2}=1$, $H_{\rm PO, bet}=1$, and $H_{\rm HS, bet}=2$.}

>>>>

The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$ comparisons, respectively). In the example depicted in {\bf Fig~\ref{cartoon}}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed. In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explain the next section. In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs.

@@

\newcommand{\figcapa}{Example of relationships between mothers and their offspring number. The open, gray, and filled circles represent mothers, their eggs, and their offspring, respectively. The area of an open circle indicates the degree of reproductive potential of each mother (i.e., $\lambda_i$). The dotted and thin arrows denote mother--egg and egg--offspring relationships, respectively. The symbol x denotes a failure to survive at sampling. Sampled individuals are denoted with squares. Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm O, 1}=5$, $n_{\rm P, 2}=6$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$. The numbers of kinship pairs: $H_{\rm PO, bet}=1$, $H_{\rm HS, bet}=2$, $H_{\rm PO, 1}=3$, and $H_{\rm PO, 2}=2$.}
